Stack Safety as a Security Property

### 2020-07-08 main.tex

The intuition behind \citet{Skorstengaard+19}'s \iflater\bcp{I forget how to
  remove the year and just have the author names here...}\fi use of the term {\em
  local state encapsulation} is that callers should be protected from
callees: a callee should be not be able to access or overwrite private data
in the caller's stack frame. We formalize this intuition as a security
property with both confidentiality and integrity components.
%
We reflect this intuition in a formal
{\em stack confidentiality} property, which promises that a callee's
observable behavior is not affected by memory outside its stack frame
(e.g., a caller's private data or uninitialized memory).  Conversely, {\em stack
  integrity} promises that, if a function call ever returns, the caller's
stack data at the point of return will be identical to what it was before
the call.

@@

\section{Stack Safety and Unsafety by Example}
\label{sec:running-example}

We begin with a running example that will serve both to concretely
demonstrate the ``stack-unsafe'' behaviors we intend to preclude and to
ground and illustrate the formal properties and enforcement mechanisms in
later sections.

@@

Stack safety is meant to protect a caller from a malicious callee's
attempts to access private data or hijack its control flow. Our
attacker model reflects this intention: we assume that the attacker
can run arbitrary code as a caller and the enforcement mechanism
should protect against that. Hardware and timing attacks are out of
scope. \leo{Anything else to add here?}
\leo{Maybe a good place to discuss calling conventions and that they
  are essentially enforced by the policy or sth?}
\rb{Intuition that the callee can do anything in principle, but the machine will
halt if it does not follow the calling convention, etc.?}

>>>>

The intuition behind \citet{Skorstengaard+19}'s\iflater\bcp{I forget how to
  remove the year and just have the author names here...}\fi use of the term {\em
  local state encapsulation} is that callers should be protected from
callees: a callee should be not be able to access or overwrite private data
in the caller's stack frame. We formalize this intuition as a security
property with both confidentiality and integrity components.
%
We reflect this intuition in a formal
{\em stack confidentiality} property, which promises that a callee's
observable behavior is not affected by memory outside its stack frame
(e.g., a caller's private data or uninitialized memory).  Conversely, {\em stack
  integrity} promises that, if a function call ever returns, the caller's
stack data at the point of return will be identical to what it was before
the call.

@@

\section{Stack {\underline{Un}}safety by Example}
\label{sec:running-example}

We begin with a running example that will serve both to demonstrate several
``stack-unsafe'' behaviors that our stack safety property should prohibit
and to ground the technical presentation in later sections.

@@

Stack safety is meant to protect a caller from a malicious callee's
attempts to access private data or highjack its control flow. Our
attacker model reflects this intention: we assume that the attacker
can run arbitrary code as a caller and the enforcement mechanism
should protect against that. Hardware and timing attacks are out of
scope. \leo{Anything else to add here?}
\leo{Maybe a good place to discuss calling conventions and that they
  are essentially enforced by the policy or sth?}
\rb{Intuition that the callee can do anything in principle, but the machine will
halt if it does not follow the calling convention, etc.?}
